\propertitle

### 2019-12-14 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-14T18:18:53+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The best experimental measurements of instantaneous neuronal activity use
remarkable technologies \citep{hongetal2019}, but can still only record a
very small sample of neurons -- hundreds at most -- compared to the numbers
that constitute a functionally distinguished brain region. Many
probabilistic models focus on such samples only: they neglect that the
recorded neurons are a sample from a larger population. Some probabilistic
models try to take unrecorded neurons into account, but they do so by
describing each neuron individually, thus becoming very complex
\citep{dunnetal2013,huang2015,battistinetal2017,pillowetal2008}. It would be useful to explore models
that operate in between, addressing the activity of the larger brain area
whence the sample comes, but \emph{collectively}, that is, without asking
about individual neuronal details. Such intermediate models would be useful
at least for preliminary investigations, to help us decide which hypotheses
to consider or discard for more complex and costly models, or to suggest
new hypotheses.

@@

In step~\ref{item:maxent_step} we actually use the
\emph{minimum-relative-entropy} method
\citep{hobsonetal1973,csiszar1985}[\sect~5.2.2]{sivia1996_r2006} with
respect to a uniform reference distribution. We shall still call it
\enquote{maximum-entropy} for brevity. It amounts to two prescriptions:
first, take the distributions satisfying specific convex constraints --
such as fixed expectations -- and among them select the one having minimum
relative entropy with respect to a reference distribution; second, judge --
and therefore set -- those expectations to be equal to some measured
averages, typically time averages. (A judgement is required because
probability expectations and empirical averages are numerically
different in general; a misjudgement of their approximate equality can lead to
\enquote{silly answers}, to quote Mackay \cite*[p.~308]{mackay1995_r2003}.)

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-14T18:54:42+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The best experimental measurements of instantaneous neuronal activity use
remarkable technologies \citep{hongetal2019}, but can still only record a
very small sample of neurons -- hundreds at most -- compared to the numbers
that constitute a functionally distinguished brain region. Many
probabilistic models focus on such samples only: they neglect that the
recorded neurons are a sample from a larger population. Some probabilistic
models try to take unrecorded neurons into account, but they do so by
describing each neuron individually, thus becoming very complex
\citep{pillowetal2008,dunnetal2013,tyrchaetal2014,huang2015,battistinetal2017}.
It would be useful to explore models that operate in between, addressing
the activity of the larger brain area whence the sample comes, but
\emph{collectively}, that is, without asking about individual neuronal
details. Such intermediate models would be useful at least for preliminary
investigations, to help us decide which hypotheses to consider or discard
for more complex and costly models, or to suggest new hypotheses.

@@

In step~\ref{item:maxent_step} we actually use the
\emph{minimum-relative-entropy} method
\citep{hobsonetal1973,csiszar1985}[\sect~5.2.2]{sivia1996_r2006} with
respect to a uniform reference distribution. We shall still call it
\enquote{maximum-entropy} for brevity. It amounts to two prescriptions:
first, take the distributions satisfying specific convex constraints --
such as fixed expectations -- and among them select the one having minimum
relative entropy with respect to a reference distribution; second, judge --
and therefore set -- those expectations to be equal to some measured
averages, typically time averages. (A judgement is required because
probability expectations and empirical averages are numerically
different in general; a misjudgement of their approximate equality can lead to
\enquote{silly answers}, to quote MacKay \citep[p.~308]{mackay1995_r2003}.)
